On centrality of orthogonal $\Kt$

### 2016-05-12 paper.tex
Many fixes

Recall that to each reduced irreducible root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$.
By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, and Steinberg relations (see~\cref{sec:prelim}). 
Thus, there is a well-defined map $\phi\colon\St(\Phi, R)\to \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image is $\E(\Phi, R)$.

@@

\section{Preliminaries} \label{sec:prelim}
Throughout this paper $R$ denotes an associative commutative ring with identity.
All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$.

@@

We denote by $R^n$ the free $R$-module with basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$ 
whose entries generate $R$ as an ideal.

As usual, $\E(n, R)=\E(\rA_{n-1}, R)$ denotes the elementary group, i.\,e. the subgroup of the general linear group $\GL(n, R)$ generated by transvections
$t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$,
where 1 stands for the identity matrix and $e_{ij}$ for the matrix unit.

The Steinberg group $\St(n, R) = \St(\rA_{n-1}, R)$ is the group defined by generators
$x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R\}$ and relations
\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\begin{align}
&x_{ij}(r)x_{ij}(s)=x_{ij}(r+s), \label{add0}\\
&[x_{ij}(r),\,x_{hk}(s)]=1,\text{ for }h\neq j,\ k\neq i, \label{ccf1}\\
&[x_{ij}(r),\,x_{jk}(s)]=x_{ik}(rs) \label{ccf2}.
\end{align}
The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.

@@

For a general $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
For more information regarding the general case we refer the reader to \cite[Section~3]{SCh}.

\section{Main reduction} \label{sec:patching}
First of all, we recall how \cref{tm:lg-principle} is proved in~\cite{Tul,SCh}.

\begin{df}
We say that the Steinberg group functor $\St(\Phi, -)$ satisfies {\it Tulenbaev lifting property} if for any ring $R$ and any non-nilpotent element $a \in R$
there exists a map $T$ which fits into the following commutative diagram.
\numberwithin{equation}{section}
\setcounter{equation}{1}
\begin{equation} \xymatrix{\St(\Phi,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(\Phi, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
                           \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
Here $\lambda_a^*$ denotes the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.                           
Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
\end{df}
It is clear that the image of $T$ is contained in the image of the top arrow, therefore, Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.

We claim that the main results of the paper follow from Tulenbaev's lifting property.
\begin{prop} Consider the following statements:
\begin{enumerate}
 \item the Steinberg group functor $\St(\Phi, -)$ satisfies lifting property~\eqref{eq:diagram};
 \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(h) = 1 \in \St(\Phi, R_a[X])$ then
       for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
 \item a local global principle for $\Kt$ holds for $\St(\Phi, -)$;
 \item centrality of $\Kt$ holds for $\St(\Phi, -)$.
\end{enumerate}
Then for any irreducible $\Phi$ of rank $\geq 2$ there are implications $a) \implies b) \implies c) \implies d)$. \end{prop}
\begin{proof} The specified implications are contained in the proofs of Lemma~15, Theorem~2 and Theorem~1 of \cite{SCh}, respectively. \end{proof}

In order to check the lifting property~\eqref{eq:diagram} one needs to have some description of the relative Steinberg group $\St(\Phi, R, I)$ by means of generators and relations.
In~\cite{Tul} another presentation was used for this purpose. We recall the details of this presentation in the next section.
On the other hand, in~\cite{SCh} the second-named author used an amalgamation theorem for the relative Steinberg group on which we now focus our attention.

For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of root subsystems of $\Phi$.
Its objects are all root subsystems $\Psi\subseteq \Phi$ and its morphisms are in one-to-one correspondence with inclusions of the form $\Psi_1\subseteq \Psi_2$.

We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are exactly root subsystems of type $\rA_1$ or $\rA_n$. 
It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $\{\alpha, -\alpha\} \subseteq \Psi \cong \rA_3$, $\Psi \subseteq \Phi$.
Now we able to formulate the amalgamation theorem~\cite[Theorem~9]{SCh}.
\begin{tm*} \label{tm:relPres} The group $\St(\Phi, R, I)$ is isomorphic to $G:=\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$ as an abstract group. \end{tm*}

@@

In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
%Assume that $I\trianglelefteq R$ such that a short exact sequence
%\renewcommand{\theequation}{$\dagger$}
\setcounter{lm}{1}
\begin{prop}\label{prop:TulPres}
For a splitting ideal $I$ and $n\geq 4$ the group $\St(n,\,R,\,I)$ is isomorphic to the group defined by generators
$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations
\setcounter{equation}{0}
\renewcommand{\theequation}{T\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add2}\\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj2}  \\
&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R) \label{add3}.
\end{align}
Moreover, the group $\St(n, R)$ decomposes into the semidirect product $\St(n,\,R, I)\rtimes \St(n,\,R/I)$.
\end{prop}
Here $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e. matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e. ${}^g X(u,\,v) = X(\phi(\sigma(g))u, \phi(\sigma(g))^*v)$ for $g \in \St(n, R/I)$.

@@

Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - \pi(\xi)e_j),\ x_{ij}(\pi(\xi)))$. 
We have to check that $\psi$ preserves relations \eqref{add0}--\eqref{ccf2}.
For example, let us check \eqref{ccf2}. 
First of all, recall that in any semidirect product of groups one can compute the commutator of two elements in the following way:
$$[(a, b), (c, d)] = (a \cdot {}^bc \cdot {}^{bdb^{-1}}a^{-1} \cdot {}^{[b, d]}c^{-1} , [b, d]).$$
For $\xi\in R$ set $\xi' = \xi - \pi(\xi)$.
Specializing $a = X(e_i, \xi' e_j)$, $b = x_{ij}(\pi(\xi))$, $c = X(e_j, \eta'e_k)$, $d = x_{jk}(\pi(\eta))$ and using the definition of the conjugation action 
one computes the commutator $[\psi(x_{ij}(\xi), \psi(x_{jk}(\eta)]$ as follows:
\setcounter{equation}{2}
\begin{equation} \left(X(e_i, \xi' e_j) \cdot X(e_j + \pi(\xi)e_i, \eta'e_k) \cdot X(e_i, \pi(\eta)\xi' e_k - \xi' e_j) \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta))\right). \label{eq:proofS3}\end{equation}
\setcounter{lm}{3}
After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, -\xi' e_j)$ to the left hand side of the formula by means of relation \eqref{conj2}
one gets the following expression
$$(X(e_j, \eta'e_k) \cdot X(e_i, (\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')e_k \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta)).$$
Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
Verification of the fact that $\psi$ preserves relations \eqref{add0}, \eqref{ccf1} is similar to the above computation but is easier.
In particular, one does not need to use relation~\eqref{add3}.

@@

Since $\pi^*(\iota(F(u, v))) = X(\pi(u),\,0)=1$ and $\pi^*(\iota(S(u,v)) = Y(0,\,\pi(v)) = 1$ we get that $\mathrm{Im}(\iota)\subseteq\Ker(\pi^*)=\St(n,\,R,\,I)$. 
It is clear that $\iota\kappa=\mathrm{id}$ hence $\kappa$ is injective.
On the other hand, $\kappa$ is surjective by Lemma~\ref{allyouneedisf}\,$(\mathrm a)$.
Thus, we have the following result.

@@

\section{The local-global principle for $\Kt$.} \label{sec:lgp}
%At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
Now we turn to the main result of this paper, namely, we construct for $n\geq 4$ the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
BLAH-BLAH-BLAH

>>>>

Recall that to each reduced irreducible root system $\Phi$ and a commutative ring $R$ one can associate a split simple group $\GG(\Phi, R)$ called a \emph{Chevalley group}.
The {\it elementary group} $\E(\Phi, R)$ is defined as the subgroup of $\GG(\Phi, R)$ generated by elementary root unipotents $t_\alpha(\xi)$, $\xi\in R$, $\alpha\in \Phi$, see~\cite{Ta, St78}.
By definition, the Steinberg group $\St(\Phi, R)$ is presented by generators $x_\alpha(\xi)$, which model the unipotents $t_\alpha(\xi)$, and Steinberg relations (see~\cref{sec:prelim}). 
Thus, there is a well-defined map $\phi\colon\St(\Phi, R)\to \GG(\Phi, R)$ sending $x_\alpha(\xi)$ to $t_\alpha(\xi)$ whose image is $\E(\Phi, R)$.

@@

\section{Preliminaries} \label{sec:prelim}
Throughout this paper $R$ denotes an associative commutative ring with identity.
All commutators are left-normed, i.\,e. $[x,\,y]=xyx\inv y\inv$. 
We denote by $R^n$ the free $R$-module with basis $e_1,\ldots,e_n$ and by $\Um(n,\,R)$ the subset of unimodular columns $v\in R^n$ 
whose entries generate $R$ as an ideal.

@@

First of all, recall that for a simply laced root system $\Phi$ of rank $\geq 2$ the Steinberg group $\St(\Phi, R)$ 
is defined by generators $x_\alpha(r)$, $\alpha\in\Phi$, $r\in R$ and the following relations:
\begin{align}
 x_\alpha(r) x_\alpha(s) & = x_\alpha(r+s) & \nonumber \\
 [x_\alpha(r),  x_\beta(s)] & = x_{\alpha+\beta}(N_{\alpha,\beta} rs) &\ \alpha,\beta\in \Phi,\ \alpha+\beta\in\Phi \nonumber \\
 [x_\alpha(r),  x_\beta(s)] & = 1 &\ \alpha,\beta\in \Phi,\ \alpha+\beta\not\in\Phi \nonumber
\end{align}
Here $N_{\alpha,\beta}$ are the structure constants of $\Phi$ which are equal to $\pm 1$.
In the case $\Phi=\rA_\ell$ we use a more common notation for root unipotents: $x_{ij}(r)$, $1\leq i\neq j\leq n$, $r\in R$,
\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\begin{align}
x_{ij}(r)x_{ij}(s)      & = x_{ij}(r+s),& \label{add0}\\
[x_{ij}(r),\,x_{hk}(s)] & = 1,& \text{ for }h\neq j,\ k\neq i, \label{ccf1}\\
[x_{ij}(r),\,x_{jk}(s)] & = x_{ik}(rs)& \label{ccf2}.
\end{align}
We denote by $\E(n, R)=\E(\rA_{n-1}, R)$ the elementary subgroup of $\SL(n, R)$, i.\,e. the subgroup generated by elementary transvections $t_{ij}(r)=1+r \cdot e_{ij}$, $1\leq i\neq j\leq n$, $r\in R$.
Here $1$ denotes the identity matrix and $e_{ij}$ is the standard matrix unit. The natural projection $\phi\colon\St(n,\,R)\rightarrow\E(n,\,R)$ sends $x_{ij}(r)$ to $t_{ij}(r)$.

@@

For arbitrary $I$ the relative Steinberg group $\St(\Phi, R, I)$ is no more a subgroup of $\St(\Phi, R)$ and should be defined as a central extension of the above kernel.
For the purposes of the present text it suffices to consider only relative Steinberg groups corresponding to splitting ideals.
For more information regarding the general case we refer the reader to \cite[Section~3]{SCh}.

\section{Reduction to the case \texorpdfstring{$\rA_3$}{A3}} \label{sec:patching}
First, we make the following definition inspired by Lemmas~2.3,~3.2 of~\cite{Tul}.

\begin{df} \label{df:tlp}
We say that the Steinberg group functor $\St(\Phi, -)$ satisfies {\it Tulenbaev lifting property} if for any ring $R$ and any non-nilpotent element $a \in R$
there exists a map $T_\Phi$ which fits into the following commutative diagram.
\numberwithin{equation}{section}
\setcounter{equation}{1}
\begin{equation} \xymatrix{\St(\Phi,\,R\ltimes XR_a[X],\,XR_a[X]) \ar@{^{(}->}[r] \ar[d]_-{\lambda_a^*} & \St(\Phi, R \ltimes XR_a[X]) \ar[d]_-{\lambda_a^*} \\
                           \St(\Phi,\,R_a[X],\,XR_a[X]) \ar@{-->}[ru]_-{T_\Phi} \ar@{^{(}->}[r] & \St(\Phi, R_a[X])} \label{eq:diagram} \end{equation}
Here $\lambda_a^*$ denotes the morphism of Steinberg groups induced by the morphism $\lambda_a\colon R \to R_a$ of localisation by the powers of $a$.                           
Notice that $XR_a[X]$ is a splitting ideal for both $R_a[X]$ and $R \ltimes XR_a[X]$.
\end{df}
It is clear that the image of $T_\Phi$ is contained in the image of the top arrow, therefore, Tulenbaev lifting property implies that the relative Steinberg groups in the left-hand side of the diagram are isomoprhic.

We claim that the main results of this paper follow from Tulenbaev's lifting property.
\begin{prop} Consider the following statements:
\begin{enumerate}
 \item the Steinberg group functor $\St(\Phi, -)$ satisfies lifting property~\eqref{eq:diagram};
 \item a dilation principle holds for $\St(\Phi, -)$, i.\,e. if $g\in\St(\Phi, A[X], XA[X])$ is such that $\lambda_a^*(h) = 1 \in \St(\Phi, R_a[X])$ then
       for sufficiently large $n$ one has $ev_{X = a^n Y}^*(h) = 1 \in \St(\Phi, A[Y])$, where $ev_{X=a^n Y}$ denotes the unique $R$-algebra morphism $R[X]\to R[Y]$ sending $X$ to $a^nY$;
 \item Quillen's local global principle for $\Kt$ holds for $\St(\Phi, -)$;
 \item the centrality of $\Kt$ holds for $\St(\Phi, -)$.
\end{enumerate}
Then for any irreducible $\Phi$ of rank $\geq 2$ there are implications $a) \implies b) \implies c) \implies d)$. \end{prop}
\begin{proof} The specified implications are contained in the proofs of Lemma~15, Theorem~2 and Theorem~1 of \cite{SCh}, respectively. \end{proof}

In order to construct the arrow $T_\Phi$ fitting in the diagram~\eqref{eq:diagram} one needs to have some direct description of the relative Steinberg group $\St(\Phi, R, I)$.
For example, in~\cite{Tul} Tulenbaev uses a variant of of W.~van~der~Kallen's ``another presentation'' for this purpose. The details of this approach are outlined in the next section.
On the other hand, in~\cite{SCh} the second-named author obtained a theorem which asserts that the relative Steinberg group $\St(\Phi, R, I)$ can be presented as an amalgamated product of
several copies of relative Steinberg groups of smaller rank.

To formulate this theorem we will need several technical definitions.
For a simply laced root system $\Phi$ we denote by $\catname{Subsys}(\Phi)$ the category of root subsystems of $\Phi$.
Its objects are all root subsystems $\Psi\subseteq \Phi$ and its morphisms are in one-to-one correspondence with inclusions of the form $\Psi_1\subseteq \Psi_2$.
It is clear that the relative Steinberg group can be turned into a functor $\St(-, R, I)\colon \catname{Subsys}(\Phi) \rightarrow\catname{Groups}.$

We denote by $\mathcal{G}_{1,n}$ the full subcategory of $\catname{Subsys}(\Phi)$ whose objects are root subsystems $\Psi\subseteq \Phi$ having type $\rA_1$ or $\rA_n$. 
It is easy to see that $\mathcal{G}_{1,n}$ is a directed bipartite graph whose only nonidentical morphisms are inclusions of the form $i_{\alpha, \Psi}\colon \{\alpha, -\alpha\} \subseteq \Psi \cong \rA_3$, $\Psi \subseteq \Phi$.
\begin{tm*} \label{tm:relPres} For a simply laced irreducible root system $\Phi$ of rank $\geq 3$
the group $\St(\Phi, R, I)$ is isomorphic as an abstract group to $\varinjlim_{\mathcal{G}_{1,3}}\St(-, R, I)$. \end{tm*}
\begin{proof} See~\cite[Theorem~9]{SCh} \end{proof}

The above theorem allows one to construct the arrow $T_\Phi$ by means of the universal property of colimits.
More precisely, one needs to construct the maps $T_{\Psi}$ for subsystems $\Psi\subseteq\Phi$ of type $\rA_3$ and then check that
relations $T_\Psi \circ i_{\alpha, \Psi} = T_{\Psi'} \circ i_{\alpha, \Psi'}$ hold for all $\Psi$, $\Psi'$ of type $\rA_3$ containing a common root $\alpha$
(here $i_{\alpha, \Psi}$ denotes the obvious morphism $\St(\{\alpha, -\alpha\}, R, I) \to \St(\Psi, R, I)$).
The latter check is relatively formal and, essentially, has already been made in~\cite{SCh} 
(see the proof of Lemma~14 and notice that everywhere in it $\rA_4$'s can be replaced with $\rA_3$'s).
On the other hand, constructing $T_\Psi$ for $\Psi=\rA_3$ is not at all obvious and will be done in the section to follow.

Summing up the above discussion, we have shown that both \cref{tm:centrality} and \cref{tm:lg-principle} follow from Tulenbaev's lifting property in the special case $\Phi=\rA_3$.

@@

In order to construct the arrow $T$ Tulenbaev uses the following presentation for the relative Steinberg group, see~\cite[Proposition~1.6]{Tul}. 
%Assume that $I\trianglelefteq R$ such that a short exact sequence
%\renewcommand{\theequation}{$\dagger$}
\setcounter{lm}{1}
\begin{prop}\label{prop:TulPres}
For a splitting ideal $I$ and $n\geq 4$ the group $\St(n,\,R,\,I)$ is isomorphic to the group defined by generators
$$\{X(u,\,v)\mid u\in\E(n,\,R)e_1,\ v\in I^n,\ u^tv=0\}$$ and the following set of relations:
\setcounter{equation}{0}
\renewcommand{\theequation}{T\arabic{equation}}
\begin{align}
&X(u,\,v)X(u,\,w)=X(u,\,v+w), \label{add2}\\
&X(u,\,v)X(u',\,v')X(u,\,v)\inv=X(t(u,\,v)u',\,t(v,\,u)\inv v'), \label{conj2}  \\
&X(ur+w,\,v)=X(u,\,vr)X(w,\,v)\,\text{ for }r\in R,\ (u,\,w)\in\Um_{n\times2}(R) \label{add3}.
\end{align}
Moreover, the group $\St(n, R)$ decomposes into the semidirect product $\St(n,\,R, I)\rtimes \St(n,\,R/I)$.
\end{prop}
Here $\Um_{n\times2}(R)$ denotes the set of $n\times2$ \emph{unimodular matrices}, i.\,e. matrices $M$ such that there exists a $2\times n$ matrix $N$ satisfying $NM=\begin{pmatrix}1&0\\0&1\end{pmatrix}$.
In the definition of the semidirect product the group $\St(n, R/I)$ acts on $\St(n, R, I)$ by conjugation via the splitting map, i.\,e. ${}^g X(u,\,v) = X(\phi(\sigma(g))u, \phi(\sigma(g))^*v)$ for $g \in \St(n, R/I)$.

@@

Define the map $\psi$ by $\psi(x_{ij}(\xi)) = (X(e_i, (\xi - \pi(\xi)e_j),\ x_{ij}(\pi(\xi)))$. 
We have to check that $\psi$ preserves relations \eqref{add0}--\eqref{ccf2}.
For example, let us check \eqref{ccf2}. 
First of all, recall that in any semidirect product of groups one can compute the commutator of two elements in the following way:
$$[(a, b), (c, d)] = (a \cdot {}^bc \cdot {}^{bdb^{-1}}a^{-1} \cdot {}^{[b, d]}c^{-1} , [b, d]).$$
For $\xi\in R$ set $\xi' = \xi - \pi(\xi)$.
Specializing $a = X(e_i, \xi' e_j)$, $b = x_{ij}(\pi(\xi))$, $c = X(e_j, \eta'e_k)$, $d = x_{jk}(\pi(\eta))$ and using the definition of the conjugation action 
one computes the commutator $[\psi(x_{ij}(\xi), \psi(x_{jk}(\eta)]$ as follows:
\setcounter{equation}{2}
\begin{equation} \left(X(e_i, \xi' e_j) \cdot X(e_j + \pi(\xi)e_i, \eta'e_k) \cdot X(e_i, \pi(\eta)\xi' e_k - \xi' e_j) \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta))\right). \label{eq:proofS3}\end{equation}
\setcounter{lm}{3}
After applying additivity relations \eqref{add2}, \eqref{add3} and moving the factor $X(e_i, -\xi' e_j)$ to the left hand side of the formula by means of relation \eqref{conj2}
one gets the following expression:
$$(X(e_j, \eta'e_k) \cdot X(e_i, (\xi' \eta' + \pi(\xi)\eta' + \pi(\eta)\xi')e_k \cdot X(e_j, -\eta'e_k),\ x_{ik}(\pi(\xi\eta)).$$
Since $\xi'\eta' + \pi(\xi)\eta' + \pi(\eta)\xi' = \xi\eta - \pi(\xi\eta)$ the above expression clearly simplifies to $\psi(x_{ik}(\xi\eta))$, as claimed.
Verification of the fact that $\psi$ preserves relations \eqref{add0}, \eqref{ccf1} is similar to the above computation but is easier.
In particular, one does not need to use relation~\eqref{add3}.

@@

Since $\pi^*(\iota(F(u, v))) = X(\pi(u),\,0)=1$ and $\pi^*(\iota(S(u,v)) = Y(0,\,\pi(v)) = 1$ we get that $\mathrm{Im}(\iota)\subseteq\Ker(\pi^*)=\St(n,\,R,\,I)$. 
It is clear that $\iota\kappa=\mathrm{id}$ hence $\kappa$ is injective.
On the other hand, $\kappa$ is surjective by Lemma~\ref{allyouneedisf}\,$(\mathrm a)$.
Thus, we have demonstrated the following result.

@@

\section{The local-global principle for \texorpdfstring{$\Kt$}{K2}}\label{sec:lgp}
%At this point we have demonstrated for $n\geq4$ and a splitting ideal $I$ that $\St^*(n,\,R,\,I)$ and $\St(n,\,R,\,I)$ are isomorphic.
Now we turn to the main result of this paper, namely, we construct for $n\geq 4$ the map $$T\colon\St(n,\,R_a[X],\,XR_a[X])\rightarrow\St(n,\,R\ltimes XR_a[X]),$$ that fits into the diagram \eqref{eq:diagram}.
